---
title: "Pricing on AWS"
output: html_document
date: '2022-10-11'
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
# amount of data to store in Gb
EA.backups <- 36300
# by type of storage price in $ a Gb/month, in months that have to be paid (minimum storage duration)
S3.Glacier.Flexible.Retrieval <- c(0.0036, 6)
S3.Glacier.Deep.Archive  <- c(0.00099, 6)
```

Estimation of the EAMENA storage cost in AWS to find the best storage service for back-up data. Today, the size of the back-up data is `r EA.backups` Gb

## S3.Standard
> currently used by EAMENA to store back-ups

-   Observed cost (current cost) in \$/month: **855.86**

-   Simulation with <https://calculator.aws/>:

```
    Tiered price for: 36300 GB
    36300 GB x 0.0230000000 USD = 834.90 USD
    Total tier cost = 834.9000 USD (S3 Standard storage cost)
    S3 Standard cost (monthly): 834.90 USD
    S3 Standard cost (upfront): 0.00 USD
```
    
## S3.Glacier.Deep.Archive

-   Estimation based on internet documentation:

```{r glacier.deep}
S3.Glacier.by.month <- EA.backups*S3.Glacier.Deep.Archive[1] # by month
S3.Glacier.minimum.plus <- (S3.Glacier.by.month)*S3.Glacier.Deep.Archive[2] # supplementary cost
```

Cost in \$/month: **`r S3.Glacier.by.month`** ~~+ supplementary cost: `r S3.Glacier.minimum.plus`~~

-   Simulation with <https://calculator.aws/>:

```
    Unit conversions
    S3 Glacier Deep Archive Average Object Size: 16 MB x 0.0009765625 GB in a MB = 0.015625 GB
    Pricing calculations
    36,300 GB per month / 0.015625 GB average item size = 2,323,200.00 unrounded number of objects
    Round up by 1 (2323200.0000) = 2323200 number of objects
    2,323,200 number of objects x 32 KB = 74,342,400.00 KB overhead
    74,342,400.00 KB overhead / 1048576 KB in a GB = 70.898438 GB overhead
    70.898438 GB overhead x 0.00099 USD = 0.0701895 USD (Glacier Deep Archive storage overhead cost for metadata)
    Glacier Deep Archive storage overhead cost: 0.0701895 USD
    2,323,200 number of objects x 8 KB = 18,585,600.00 KB overhead
    18,585,600.00 KB overhead / 1048576 KB in a GB = 17.724609 GB overhead
    Tiered price for: 17.724609 GB
    17.724609 GB x 0.0230000000 USD = 0.41 USD
    Total tier cost = 0.4076660 USD (S3 Standard storage overhead cost)
    S3 Standard storage overhead cost: 0.407666 USD
    36,300 GB per month x 0.00099 USD = 35.937 USD (Glacier Deep Archive storage cost)
    Glacier Deep Archive storage cost: 35.937 USD
    0.0701895 USD + 0.407666 USD + 35.937 USD = 36.414856 USD (Total Glacier Deep Archive storage cost)
    30 requests x 0.000055 USD = 0.0016 USD (Cost for Lifecycle transitions)
    36.414856 USD + 0.0016 USD = 36.42 USD (S3 Glacier Deep Archive cost)
    **S3 Glacier Deep Archive cost (monthly): 36.42 USD**
    S3 Glacier Deep Archive cost (upfront): 0.00 USD
```

## S3.Glacier.Flexible.Retrieval

> formely: Glacier

-   Estimation based on internet documentation:

```{r glacier.flex}
S3.Glacier.by.month <- EA.backups*S3.Glacier.Flexible.Retrieval[1] # by month
S3.Glacier.minimum.plus <- (S3.Glacier.by.month)*S3.Glacier.Flexible.Retrieval[2] # supplementary cost
```

Cost in \$/month: **`r S3.Glacier.by.month`** ~~+ supplementary cost: `r S3.Glacier.minimum.plus`~~

-   Simulation with <https://calculator.aws/>:

```
36,300 GB x 0.004 USD = 145.20 USD (S3 Glacier Instant Retrieval storage cost)
S3 Glacier Instant Retrieval cost (monthly): 145.20 USD
```
